---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r library, echo = FALSE}
library(stringr)
library(glue)
# install.packages("remotes")
# remotes::install_github("gadenbuie/epoxy")
library(epoxy)
```


# resources

<!-- badges: start -->
[![Netlify Status](https://api.netlify.com/api/v1/badges/be8234bf-10d0-431b-bf4c-c03acef359fd/deploy-status)](https://app.netlify.com/sites/numbat-resources/deploys)
<!-- badges: end -->

This page exists to help collate together R resources for the NUMBATs group, to direct students to places to learn more about specific R content. It is not intended as a replacement for courses, but instead a place where people can go to learn more.

The core principles for the resources on this page are:

- Content should be fresh and relevant, rooted in practical example, "why should we care"
- The way these resources are distributed should be:
  - Accessible, reproducible, extendible
- Links shared must work

# Current areas covered

The current areas covered are:

```{glue}
# - {topic_list}
```

# Got an idea? Want a resource on a particular area? 

- You can [submit an issue](https://github.com/numbats/resources/issues/new)
- You can contribute by [editing the rmd directly]() or forking and making a pull request
- Ping Nick Tierney on the NUMBATs Slack
