---
title: "Ari example"
author: 
  - "Nicholas Tierney"
date: '`r Sys.Date()`'
output: ioslides_presentation
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
# library(xaringanthemer)
# style_duo_accent(
#   primary_color = "#1381B0",
#   secondary_color = "#FF961C",
#   inverse_header_color = "#FFFFFF"
# )
```

<!-- This is the title slide -->

## Using ari

<!-- 
G'day!!! This is an example usage of generating content for ari.
-->

## Create a HTML slide deck

For example, with the **xaringan** package.

```{r eval=FALSE, tidy=FALSE}
install.packages("xaringan")
```

Use [RStudio IDE](https://www.rstudio.com/products/rstudio/):

- Create a new R Markdown document from the menu `File -> New File -> R Markdown -> From Template -> Ninja Presentation`

<!-- 
Create a slide deck 
-->

## Create a HTML slide deck

- Every slide should have HTML comments for each slide (although you can also have a separate script file with the same headings)

```

# Here is a slide title

- And here is some slide text

`<!--`
And here is the HTML comment that forms your script
`-->`

```

- Ensure Rmd is knitted into HTML - Click the `Knit` button to compile it;

<!-- And here is the HTML comment that forms your script -->

## Create a HTML slide deck

- Install the `aws.polly` package from CRAN

```r
install.packages("aws.polly")
```

You then need to set up an account with AWS if you haven't already

Sean Kross has a great [write up of doing that](http://seankross.com/2017/05/02/Access-Amazon-Web-Services-in-R.html).

  - that example is realted to S3 however, what you want to do is search for
  "polly" and then

<!-- 
Install the AWS polly package from CRAN 
-->

## Math Expressions

A Linear model is given by 

$$\hat{Y}=\beta_0 + \beta_1 x_1 + \epsilon$$

<!-- A linear model is given by an intercept, beta nought, plus some slope, beta 1 ex 1, plus some error term, epsilon. -->

## R Code

```{r comment='#'}
# a boring regression
fit = lm(dist ~ 1 + speed, data = cars)
coef(summary(fit))
```

<!-- Here is an example of some R code -->

## R Plots

```{r cars, fig.height=4, dev='svg'}
par(mar = c(4, 4, 1, .1))
plot(cars, pch = 19, col = 'darkgray', las = 1)
abline(fit, lwd = 2)
```

<!-- Here is an example of an R plot -->

## Tables

If you want to generate a table, make sure it is in the HTML format (instead of Markdown or other formats), e.g.,

```{r}
knitr::kable(head(iris), format = 'html')
```

<!-- Here is an example of a table -->

## Thanks!

Slides created via the R package [**xaringan**](https://github.com/yihui/xaringan).

The chakra comes from [remark.js](https://remarkjs.com), [**knitr**](http://yihui.name/knitr), and [R Markdown](https://rmarkdown.rstudio.com).

<!-- 
Thanks for listening! 

The slides were created with the R package, xaringan, 

And my narration was made possible with the "ari" package, from Johns Hopkins Data Science Lab.

Special thanks to Sean Kross, and John Muschelli
-->